All Gene Supplementary Material - Additional samples removed.

### 2017-11-08 all_gene_analysis/all_gene_analysis_additional_treatment_removed.Rmd
added in analysis with additional isolates excluded that had previously been treated. This was in response to reviewer comments

---
title: "All Gene Supplementary Material"
author: "Gerry Tonkin-Hill"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_width: 12
    fig_height: 8
---

@@

###Remove drug treated samples
Samples SFU2 and SFU3 were drug treated and are removed.
```{r}
x$counts <- x$counts[,!grepl("SFU2|SFU\\.3", colnames(x$counts))]
filt.annnotation <- fc2$annotation[fc2$annotation$GeneID %in% rownames(x$counts),]
dge <- DGEList(counts=x$counts, genes=filt.annnotation)

```

>>>>

---
title: "All Gene Supplementary Material - Additional samples removed."
author: "Gerry Tonkin-Hill"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_width: 12
    fig_height: 8
---

@@

###Remove drug treated samples
Samples SFU2 and SFU3 were drug treated and are removed. We repeated the analysis of the all gene DGE omitting a few patients who had anti-malarial treatments in preceding months. The patients omitted are: SFM 007, SFC 023, IFM 012 and IFM 021.
```{r}
x$counts <- x$counts[,!grepl("SFU2|SFU\\.3", colnames(x$counts))]
x$counts <- x$counts[,!grepl("SFM\\.7|SFC\\.023|IFM12|IFM21", colnames(x$counts))]
filt.annnotation <- fc2$annotation[fc2$annotation$GeneID %in% rownames(x$counts),]
dge <- DGEList(counts=x$counts, genes=filt.annnotation)
```
